\textls[-0]{\thetitle}

### 2023-03-07 metatheory2.tex
Working on examples.

So we can inductively define the syntax sugar $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ using constructors $\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$. Then we define the $\inh{h}{\ell}$ and the explicit substitution for linkage transformer $\sub{h}{\gm}$ by induction on the structure of linkage transformer $h$, based on the equality\EDJ{Add substitution equalities for linkage transformers} given in the syntax. In that way, the explicit substituon for linkage transformer becomes meta-level substitution again; and $\inh{h}{\ell}$ is not itself a syntax but a meta-level computation that leads to a syntax.

>>>>

So we can inductively define the syntax sugar $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ using constructors $\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$. Then we define the $\inh{h}{\ell}$ and the explicit substitution for linkage transformer $\sub{h}{\gm}$ by induction on the structure of linkage transformer $h$, based on the equality
%\EDJ{Add substitution equalities for linkage transformers} 
given in the syntax. In that way, the explicit substituon for linkage transformer becomes meta-level substitution again; and $\inh{h}{\ell}$ is not itself a syntax but a meta-level computation that leads to a syntax.
